Plant-pollintor networks worldwide are composed by the same specific building blocks

### 2021-05-18 Draft/Draft.Rmd
Update Draft.Rmd

#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
#NICE! Can we put motifs in Y axes, and % in X?
```
2) FG-position associations.
```{r}
library(lme4)
library(nlme)
library(tidyverse)
library(stringi)
source("../Scripts/Scripts_Alfonso/add_study_id.R")

@@

ggplot(NULL) + 
  geom_point(data = plant_position_percentiles_filtered,
             aes(x=as.factor(position), y=percentil_its_GF, 
                 color = as.factor(position)),
             position = "jitter",alpha=0.5)+
  facet_wrap(~Node_FG)+
  geom_errorbar(data = plant_means,aes(x = as.factor(position), ymin=mean-SE, ymax=mean+SE), 
                width=1.0,size=1)+
  geom_point(data = plant_means,aes(x = as.factor(position), y=mean), 
                size=2)+
  labs(x="Position", y = "Percentile",title = "Pollinators")+
  theme_bw()+
  theme(legend.position = "none",axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))

@@

ggplot(NULL) + 
  geom_point(data = pollinator_position_percentiles_filtered,
             aes(x=as.factor(position), y=percentil_its_GF, 
                 color = as.factor(position)),
             position = "jitter",alpha=0.5)+
  facet_wrap(~Node_FG)+
  geom_errorbar(data = pollinator_means,aes(x = as.factor(position), ymin=mean-SE, ymax=mean+SE), 
                width=1.0,size=1)+
  geom_point(data = pollinator_means,aes(x = as.factor(position), y=mean), 
                size=2)+
  labs(x="Position", y = "Percentile", title = "Pollinators")+
  theme_bw()+
  theme(legend.position = "none",axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))

>>>>

#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
#NICE! Can we put motifs in Y axes, and % in X?
```
2) FG-position associations.
```{r}
library(lme4)
library(nlme)
library(tidyverse)
library(stringi)
library(ggpubr)
source("../Scripts/Scripts_Alfonso/add_study_id.R")

@@

GF_plant_pos <- ggplot(NULL) + 
  geom_point(data = plant_position_percentiles_filtered,
             aes(x=as.factor(position), y=percentil_its_GF, 
                 color = as.factor(position)),
             position = "jitter",alpha=0.5)+
  facet_wrap(~Node_FG)+
  geom_errorbar(data = plant_means,aes(x = as.factor(position), ymin=mean-SE, ymax=mean+SE), 
                width=1.0,size=1)+
  geom_point(data = plant_means,aes(x = as.factor(position), y=mean), 
             size=2)+
  labs(x="Position", y = "Percentile",title = "Pollinators")+
  theme_bw()+
  theme(legend.position = "none",axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
  library(lme4)
library(nlme)
library(tidyverse)
library(stringi)
library(ggpubr)
source("Scripts/Scripts_Alfonso/add_study_id.R")

all_position_percentiles <- read_csv("Data/Csv/Motifs_positions_and_null_models/GF_positions_frequency_percentile.csv")

GF_plant_pos <- ggplot(NULL) + 
  geom_point(data = plant_position_percentiles_filtered,
             aes(x=as.factor(position), y=percentil_its_GF, 
                 color = as.factor(position)),
             position = "jitter",alpha=0.5)+
  facet_wrap(~Node_FG,ncol = 5)+
  geom_errorbar(data = plant_means,aes(x = as.factor(position), ymin=mean-SE, ymax=mean+SE), 
                width=1.0,size=1)+
  geom_point(data = plant_means,aes(x = as.factor(position), y=mean), 
             size=2)+
  labs(x="Position", y = "Percentile",title = "Plants")+
  theme_bw()+
  theme(legend.position = "none")+#,axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
  coord_flip()

@@

GF_poll_pos <- ggplot(NULL) + 
  geom_point(data = pollinator_position_percentiles_filtered,
             aes(x=as.factor(position), y=percentil_its_GF, 
                 color = as.factor(position)),
             position = "jitter",alpha=0.5)+
  facet_wrap(~Node_FG,ncol = 5)+
  geom_errorbar(data = pollinator_means,aes(x = as.factor(position), ymin=mean-SE, ymax=mean+SE), 
                width=1.0,size=1)+
  geom_point(data = pollinator_means,aes(x = as.factor(position), y=mean), 
             size=2)+
  labs(x="Position", y = "Percentile", title = "Pollinators")+
  theme_bw()+
  theme(legend.position = "none")+#,axis.text.x=element_text(angle=90,vjust=0.5, hjust=1))+
  coord_flip()

# Plant and Pollinators--------

ggarrange(GF_plant_pos,GF_poll_pos,
          ncol = 1, nrow = 2,heights = c(.9, 1.4))
